Space for WHAM: a multi-region, multi-stock generalization of the Woods Hole Assessment Model with an application to black sea bass

### 2025-01-02 paper/symboltable.tex
saving work

$\epsilon_{r\rightarrow r',y,a,i}$ &  random effect parameter for movement from region $r$ to region $r'$ in seasonal interval $i$ and year $y$ at age $a$\\

@@

$\epsilon_{M,r,y,a}$ & random effect parameter for natural mortality in region $r$ and year $y$ at age $a$\\

>>>>

$\varepsilon_{r\rightarrow r',y,a,i}$ &  random effect parameter for movement from region $r$ to region $r'$ in seasonal interval $i$ and year $y$ at age $a$\\

@@

$\varepsilon_{M,r,y,a}$ & random effect parameter for natural mortality in region $r$ and year $y$ at age $a$\\
